ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-09-26 rebuttal.tex

\textit{5.~Page 1, line 31: The future development plans include support for jet stirred reactors, however, this is not mentioned in section 5, Conclusions and future work, nor is there any reference to it on the GitHub wiki roadmap of PyKED.}

\textbf{Our response:}

\textit{6. I don't completely agree with the second part of the statement on page 2 line 16-18: ``Second, the XML format is intended to be a machine-readable mark-up language rather than a data format, and its lack of human readability presents a barrier to creating and working with database files.''}

\textit{In my opinion the YAML format resembles the XML format strongly. XML format is human-readable, however, because of the html-tags and `\texttt{<>} characters, the YAML format might be easier to read. If XML would lack human readability as it is stated in the article, it would not be such a popular format, and I don't think PrIMe and ReSpecTh would be using it.}

\textbf{Our response:}
We agree with the reviewer that XML is technically human readable by an expert (as opposed to, say, a binary format), and also that YAML is easier to read---by ``human-readable'', we really mean human-\emph{understandable}.

### 2017-09-26 pyked.tex
added new ref in response to #2

Nonetheless, databases of fundamental combustion experiments
have proved quite useful. For instance, Olm and colleagues used their
ReSpecTh-based database to quantify the performance of literature
hydrogen~\autocite{Olm:2014gn} and syngas~\autocite{Olm:2015ch} kinetic models,
and more recently develop improved models for hydrogen\slash
syngas~\autocite{Varga:2016gj} and ethanol~\autocite{Olm:2016et}. In all four
cases, they converted numerous experimental datasets from the literature into
the ReSpecTh standard.

>>>>

Nonetheless, databases of fundamental combustion experiments
have proved quite useful. For instance, Olm and colleagues used their
ReSpecTh-based database to quantify the performance of literature
hydrogen~\autocite{Olm:2014gn} and syngas~\autocite{Olm:2015ch} kinetic models,
and more recently develop improved models for hydrogen\slash
syngas~\autocite{Varga:2016gj}, methanol\slash formaldehyde~\autocite{Olm:2017a},
 and ethanol~\autocite{Olm:2016et}. In all four
cases, they converted numerous experimental datasets from the literature into
the ReSpecTh standard.
